Searching for flaring star-planet interactions in star-planet systems in Kepler and TESS

### 2023-03-07 src/tex/ms.tex
[showyourwork] overleaf sync

\subsubsection{Kepler-411}
\label{sec:results:individualstars:kep411}
Kepler-411 has 3 mag fainter companion~\cite{wang2014influence,ziegler2018measuring}, but we do not exclude it from the analysis. The system was observed in Kepler short cadence by \citet{jackman2021stellara} and both the planet host, and the companion star flare. \citet{jackman2021stellara} disentangle the contributions from each component on a pixel level. According to \citet{morton2016false, sun2019kepler411}, Kepler-411's planets orbit the primary companion. The fainter companion of Kepler-411 appears to cause the majority of flares (41), whereas the planet host causes only 7. We adopt the 7 flares from \cite{jackman2021stellara} in our analysis.

@@

In the scenario wherein the stretch-and-break mechanism drives the interaction, the three system cluster together most distinctly. In this scenario, they 
\subsubsection{HIP 67522}
\label{sec:results:individualstars:hip67522}
HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest signs of flaring SPI, albeit with only 6 flares in the sample. These flares are distributed across two Sectors in TESS. In Sector 11, two flares occur at orbital phases $\sim 0.6$ and $\sim 0.8$. Two years later, in Sector 38, four flares occur, but this time, all of them take place at orbital phases $0.00-0.05$, that is, up to a few hours after transit.

>>>>

\subsubsection{Kepler-411}
\label{sec:results:individualstars:kep411}
Kepler-411 has 3 mag fainter companion~\cite{wang2014influence,ziegler2018measuring}, but we do not exclude it from the analysis. The system was observed in Kepler short cadence by \citet{jackman2021stellara} and both the planet host, and the companion star flare. \citet{jackman2021stellara} disentangle the contributions from each component on a pixel level. According to \citet{morton2016false, sun2019kepler411}, Kepler-411's planets orbit the primary companion. The fainter companion of Kepler-411 appears to cause the majority of flares (41), whereas the planet host causes only 7. Adopting the 7 flares from \cite{jackman2021stellara} in our analysis, we find that they all have equivalent duration $<1\,$s, which excludes Kepler-411 from our analysis.

@@

In the scenario wherein the stretch-and-break mechanism drives the interaction, the three system cluster together most distinctly. In this scenario, most, but not all systems that do not show elevated interaction, have a weaker magnetic field~(top row in Figure\ref{fig:adtest_bp}). An excep
\subsubsection{HIP 67522}
\label{sec:results:individualstars:hip67522}
HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest signs of flaring SPI, albeit with only 6 flares in the sample. These flares are distributed across two Sectors in TESS. In Sector 11, two flares occur at orbital phases $\sim 0.6$ and $\sim 0.8$. Two years later, in Sector 38, four flares occur, but this time, all of them take place at orbital phases $0.00-0.05$, that is, up to a few hours after transit.
